\plaintitle

### 2017-04-24 delegation.tex
Splitting papers.

Two of the most shocking democratic votes in recent history occurred in 2016:
The referendum vote for Britain to leave the European Union (``Brexit'') and the election of Donald Trump as
President of the United States.
Both votes were decided by the slimmest of margins, but more significantly, both votes had poor turnout.
We often hear that the Achilles heel of a democracy is low engagement, but this is a fallacy~---~in fact, our goal
should be to decrease engagement.
The ideal governance system is one where citizens do not have to be constantly involved, but the system is still
acting as the citizens would like it to. Can we increase legitimacy within a democracy while also decreasing the
attention required at the same time?

In this paper we present our work on improving the collective decision-making through use of a web application
to facilitate the process.
In contrast with existing similar solutions, our web application integrates new ideas in how to improve this process:
use of range voting, dynamic quorum, and vote delegation.
The broad idea is that instead of just trying to move the voting process online~---~something many others have done
previously~---~we in fact wish to add value by voting online.
Specifically, we can compute results faster, more accurately,
%and securely,
we can use sophisticated statistics to
estimate important quantities for the entire voting population, we can allow for members to entrust others who have
more expertise on topics than they do themselves, and we can promote clarity and full understanding of the voting
items for all.

@@

\subsection{Range Voting}

Range voting (also known as score voting) is voting where members of a community express their positions on open proposals by assigning
each a score on a fixed scale, in the context of this paper, between $-1$ and $+1$.
A proposal passes if the average score of all votes on a position is positive.
When multiple competing proposals are being voted on, the one with highest average score wins.

Prior work has shown that this approach generalizes many previous approaches to voting and allows members to express their
positions in a highly informative and precise manner.
We find it especially suitable for a web application because many web users are used to use it when ranking products
and giving other ``five-star'' feedback.
Moreover, if later on a new proposal is added to a set of existing proposals on which voting was already open, only the
new proposal needs to be evaluated by members, as opposed to alternative voting systems where the relative rankings of
each proposal would need reassessing (assuming members use a consistent personal scale when voting).

\subsection{Dynamic Quorum}

%\todo[inline]{Unify terminology: population -> community, voters -> members, item -> proposal, motion -> proposal}

Dynamic quorum uses statistical hypothesis testing to compute the minimum number of required votes needed
to achieve a desired level of confidence before a community adopts an outcome as being truly representative of
its members' positions.
For example, in a community of 100 members, if 20 members vote in full support of a proposal, then we can conclude
with very high confidence that, had all 100 members actually voted, a majority them would support the proposal,
despite in actuality 80 members not having voted.
On the other hand, if 80 members vote but 41 vote in support of the proposal and 39 vote in opposition,
the community cannot yet conclude anything with high confidence.
Hence, the suggested action would be for the community to gather more votes and continue discussion around the proposal.
By utilizing a dynamic quorum, we can direct attention and participation of the community towards contentious proposals,
while reducing attention towards proposals which already have overwhelming support.

\subsubsection{Background}
A population of voters (a community) needs to collectively decide which item (if any) to take action on out of a set of competing items.
In order to democratically take action, the population needs to have a \{simple, super\}-majority of ``yes'' votes on a
winning item, while also demonstrating that the winning item is preferred over all other competing items.
We do not want to poll the entire population, but we do want to be certain (specifically, $99\%$ certain) that
the population does not take undesired actions, which in this case encompasses taking action on an item that is not
supported by a majority of the population and/or taking action on an item that is not clearly preferred over all
other competing alternatives.

\subsubsection{Problem Statement}
We wish to compute the probability that the bias in a population towards voting ``yes'' is greater than some
fraction of the population (e.g., $50\%$ for a simple majority, $67\%$ for a super majority).
In addition, we wish to compute the probability that the bias towards voting ``yes'' on a specific item is greater
than the bias towards voting ``yes'' on all other competing items.

\subsubsection{Assumptions}
We assume that there is a fixed underlying bias in the population that is to be estimated given raw voting data.

Without any votes, we assume that this bias may be any value between $0\%$ and $100\%$ with equal probability.

\subsubsection{Voting}
We allow for range voting where each member of the population may choose any real number in the range $[-1,+1]$ to
represent their vote, with $-1$ representing opposition and $+1$ representing support.
In the theory subsection below, we rescale votes to be in the range $[0,1]$ via the notation $\frac{votes + 1}{2}$.

We allow voters to ``abstain'' from voting.
We treat abstentions as indicating that a voter is removing themselves from the population of voters for an item.
It is important to distinguish an ``abstention'' (removing yourself from the voting population) from voting $0$
(indicating indifference).

\subsubsection{Bayesian Theory}

The commonplace and convenient choice of using the Beta distribution as our prior on the population bias is a
consequence of the Beta distribution's conjugacy with the binomial distribution, a distribution that arises
naturally when considering samples from a finite population.\footnote{To
properly understand the Bayesian approach to parameter estimation, read the following instructive tutorial:
\url{http://www.behind-the-enemy-lines.com/2008/01/are-you-bayesian-or-frequentist-or.html}
The tutorial is very similar to the problem we have at hand.}

After extracting the sufficient statistics from raw votes~---~namely the average score and the number of
abstentions~---~we can adjust the effective population size and corresponding threshold.
In addition, we can calculate the effective number of ``yes'' and ``no'' votes.\footnote{Which one can think
of as the number of Heads and Tails in the aforementioned tutorial.}

Let
\begin{description}
\begin{itemize}
\item[$C = $] $\{X_1,\ldots, X_n\}$, the set of competing motions,
\item[$N = $] population size,
\item[$X_i = $] $\{v_1, \ldots, v_{m_i}\}$, the $m_i$ raw votes for motion $X_i$, excluding ``abstentions'',
\item[$N_i = $] $(N - \textrm{number of abstentions on } X_i)$, the effective population voting on motion $X_i$,
\item[$\alpha_i = $] $\sum\limits_{v \in X_i} \left(\frac{v+1}{2}\right)$, the effective number of ``yes'' votes on motion $X_i$,
\item[$\beta_i = $] $m_i - \alpha_i$, the effective number of ``no'' votes on motion $X_i$,
\item[$K_i = $] $N_i - m_i$, the number of remaining votes yet to be cast on $X_i$,
\item[$p_i = $] true latent population bias towards voting ``yes'' on $X_i$.
\end{itemize}
\end{description}

When we have a single motion open for voting, $C=\{X_1\}$, we simply wish to compute:
\begin{align}\label{eq1}
\Pr(\alpha^*_1 > T_1 \mid X_1),
\end{align}
where
\begin{description}
\begin{itemize}
\item[$\alpha^*_i = $] the total number of ``yes'' votes for $X_i$ if we were to sample the entire population,
\item[$T_i = $] $f \cdot N_i$, for some fraction $f$ corresponding to the type of majority needed for the vote
(e.g. $f=\frac{1}{2}$ for a simple majority).
\end{itemize}
\end{description}
Using the prior $p_1 \mid X_1 \sim \operatorname{Beta}(1+\alpha_1,1+\beta_1)$, corresponding to a uniform prior when
no votes have been cast ($\alpha_1 = \beta_1 = 0$), we can express \eqref{eq1} as:
\begin{align*}
\Pr(\alpha^*_1 > T_1 \mid X_1) &= 1 - \Pr(\alpha^*_1 \leq T_1 \mid X_1),\\
\Pr(\alpha^*_1 \leq T_1 \mid X_1) &= \int_0^1 \Pr(\alpha^*_1 \leq T_1 \mid p_1)\cdot \Pr(p_1 \mid X_1) \mathrm{d}p_1\\
&= \int_0^1 \sum\limits_{i=0}^{V_1} {K_1 \choose i} p_1^{i} {(1-p_1)}^{K_1-i} \\
& \qquad\qquad\quad \times \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \mathrm{d}p_1,
\end{align*}
where
\begin{description}
\begin{itemize}
\item[$V_i = $] $\lfloor{T_i - \alpha_i}\rfloor$, the maximum number of additional ``yes'' votes allowed such that
$X_i$ would remain below threshold.
\end{itemize}
\end{description}

Hence, we have
\begin{align}\label{eq2}
& \Pr(\alpha^*_1 > T_1 \mid X_1) = \nonumber\\
& 1 - \int_0^1 \sum\limits_{i=0}^{V_1} {K_1 \choose i} p_1^{i} {(1-p_1)}^{K_1-i} \cdot \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \mathrm{d}p_1
\end{align}

In the scenario where $\mathbf{card}(C) = n > 1$, i.e., there are competing motions, there is additional complexity to
consider.
Without loss of generality, assume that $X_1$ is the most popular motion within $C$.
We now wish to not only compute \eqref{eq1}, but also the probability that $X_1$ is superior to all other
$X_i  \in C, i \neq 1$:

\begin{align}\label{eq3}
\Pr\left(\bigwedge_{i=2}^n (\alpha^*_1 > \alpha^*_i) \mid C\right)
\end{align}

Using the assumption
that votes on motions are independent across motions, which, in the common
scenario where there is a negative covariance between votes on competing
motions, will provide a lower bound on the probability, we can decompose \eqref{eq3} as follows:
\begin{align*}
& \Pr\left(\bigwedge_{i=2}^n (\alpha^*_1 > \alpha^*_i) \mid C\right)\\
=& \prod_{i=2}^n \Pr(\alpha^*_1 > \alpha^*_i \mid C)\\
=& \prod_{i=2}^n \iint\limits_{p_1, p_i} \Pr(\alpha^*_1 > \alpha^*_i \mid p_1, p_i) \cdot \Pr(p_1 \mid X_1) \cdot \Pr(p_i \mid X_i) \mathrm{d}p_i \mathrm{d}p_1\\
=& \prod_{i=2}^n \int_0^1 \int_0^1 \Pr(\alpha^*_1 > \alpha^*_i \mid p_1, p_i) \cdot \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \\
& \qquad\qquad\qquad \times \operatorname{Beta}(p_i; 1+\alpha_i,1+\beta_i) \mathrm{d}p_i \mathrm{d}p_1\\
\end{align*}
Deriving an expression for $\Pr(\alpha^*_1 > \alpha^*_i \mid p_1, p_i)$, we get:
\begin{align*}
& \Pr(\alpha^*_1 > \alpha^*_i \mid p_1, p_i)\\
=& 1 - \Pr(\alpha^*_1 \leq \alpha^*_i \mid p_1, p_i)\\
=& 1 - \sum\limits_{m=0}^{K_1} \sum\limits_{n=\lceil{v_{1,i}+m}\rceil}^{K_i} {K_1 \choose m} p_1^{m} {(1-p_1)}^{K_1 - m} \cdot {K_i \choose n} p_i^{n} {(1-p_i)}^{K_i-n},
\end{align*}
where
\begin{description}
\begin{itemize}
\item[$v_{i,j} = $] $\alpha_i - \alpha_j$, the number of effective ``yes'' votes $X_i$ leads $X_j$ by.
\end{itemize}
\end{description}

Denoting
\begin{align}\label{eq4}
& \Phi_i(p_1,p_i) {\overset {\underset {\mathrm {def} }{}}{=}} \nonumber\\
& 1 - \sum\limits_{m=0}^{K_1} \sum\limits_{n=\lceil{v_{1,i}+m}\rceil}^{K_i} {K_1 \choose m} p_1^{m} {(1-p_1)}^{K_1 - m} \cdot {K_i \choose n} p_i^{n} {(1-p_i)}^{K_i-n},
\end{align}
we can simplify \eqref{eq3} to:
\begin{align}\label{eq5}
& \Pr\left(\bigwedge_{i=2}^n (\alpha^*_1 > \alpha^*_i) \mid C\right)\nonumber\\
&= \prod_{i=2}^n \int_0^1 \int_0^1 \Phi_i(p_1,p_i) \cdot \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \nonumber\\
& \qquad\qquad\qquad \times \operatorname{Beta}(p_i; 1+\alpha_i,1+\beta_i) \mathrm{d}p_i \mathrm{d}p_1
\end{align}

We can numerically compute \eqref{eq2} and \eqref{eq5} given raw voting data.
In order to be certain before taking any actions, we would like for the computed credibilities to be $\geq 99\%$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/simple_majority}
\caption{Simple Majority: $\alpha$ vs. $\Pr(\alpha > \frac{1}{2}N)$ for $N=100$, $\beta = 10$.}
\label{simple_majority}
\end{figure}
%Data:
%Curve 1: {{0,0.000299648},{1,0.00213083},{2,0.00817989},{3,0.0224777},{4,0.049512},{5,0.0928927},{6,0.154136},{7,0.232044},{8,0.322859},{9,0.421057},{10,0.520467},{11,0.615358},{12,0.701241},{13,0.775267},{14,0.836245},{15,0.884385},{16,0.920892},{17,0.947532},{18,0.966265},{19,0.978973},{20,0.987296},{21,0.992561},{22,0.99578},{23,0.997682},{24,0.998767},{25,0.999366}}
%Curve 2: {x, 0.99} for all x

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/super_majority}
\caption{Super Majority: $\alpha$ vs. $\Pr(\alpha > \frac{2}{3}N)$ for $N=100$, $\beta = 10$.}
\label{super_majority}
\end{figure}
%Data:
%Curve 1: {{10,0.0395173},{11,0.0591278},{12,0.0846131},{13,0.116407},{14,0.15463},{15,0.199057},{16,0.24911},{17,0.303899},{18,0.362273},{19,0.422909},{20,0.484399},{21,0.545345},{22,0.604445},{23,0.660559},{24,0.712764},{25,0.760382},{26,0.802985},{27,0.840385},{28,0.872612},{29,0.899875},{30,0.922519},{31,0.940987},{32,0.955777},{33,0.967407},{34,0.976384},{35,0.983186},{36,0.988243},{37,0.99193},{38,0.994567},{39,0.996414},{40,0.997682},{41,0.998533},{42,0.999093},{43,0.999452},{44,0.999677},{45,0.999815},{46,0.999896},{47,0.999944},{48,0.99997},{49,0.999985},{50,0.999993}}
%Curve 2: {x, 0.99} for all x

%\todo[inline]{Do we take into the account the distribution of votes? So if you have a very large standard deviation
%we might want to prefer a decision less than some other decision with smaller standard deviation, but maybe
%also smaller (but still positive) average. Is distribution of votes influencing dynamic quorum?}

>>>>

%Two of the most shocking democratic votes in recent history occurred in 2016:
%The referendum vote for Britain to leave the European Union (``Brexit'') and the election of Donald Trump as
%President of the United States.
%Both votes were decided by the slimmest of margins, but more significantly, both votes had poor turnout.
%We often hear that the Achilles heel of a democracy is low engagement, but this is a fallacy~---~in fact, our goal
%should be to decrease engagement.
%The ideal governance system is one where citizens do not have to be constantly involved, but the system is still
%acting as the citizens would like it to. Can we increase legitimacy within a democracy while also decreasing the
%attention required at the same time?
%
%In this paper we present our work on improving the collective decision-making through use of a web application
%to facilitate the process.
%In contrast with existing similar solutions, our web application integrates new ideas in how to improve this process:
%use of range voting, dynamic quorum, and vote delegation.
%The broad idea is that instead of just trying to move the voting process online~---~something many others have done
%previously~---~we in fact wish to add value by voting online.
%Specifically, we can compute results faster, more accurately,
%%and securely,
%we can use sophisticated statistics to
%estimate important quantities for the entire voting population, we can allow for members to entrust others who have
%more expertise on topics than they do themselves, and we can promote clarity and full understanding of the voting
%items for all.

@@

### 2017-04-24 statistical-quorum.tex
Splitting papers.

>>>>

\section{Features}

\section{Range Voting}

Range voting (also known as score voting) is voting where members of a community express their positions on open proposals by assigning
each a score on a fixed scale, in the context of this paper, between $-1$ and $+1$.
A proposal passes if the average score of all votes on a position is positive.
When multiple competing proposals are being voted on, the one with highest average score wins.

Prior work has shown that this approach generalizes many previous approaches to voting and allows members to express their
positions in a highly informative and precise manner.
We find it especially suitable for a web application because many web users are used to use it when ranking products
and giving other ``five-star'' feedback.
Moreover, if later on a new proposal is added to a set of existing proposals on which voting was already open, only the
new proposal needs to be evaluated by members, as opposed to alternative voting systems where the relative rankings of
each proposal would need reassessing (assuming members use a consistent personal scale when voting).

\subsection{Dynamic Quorum}

%\todo[inline]{Unify terminology: population -> community, voters -> members, item -> proposal, motion -> proposal}

Dynamic quorum uses statistical hypothesis testing to compute the minimum number of required votes needed
to achieve a desired level of confidence before a community adopts an outcome as being truly representative of
its members' positions.
For example, in a community of 100 members, if 20 members vote in full support of a proposal, then we can conclude
with very high confidence that, had all 100 members actually voted, a majority them would support the proposal,
despite in actuality 80 members not having voted.
On the other hand, if 80 members vote but 41 vote in support of the proposal and 39 vote in opposition,
the community cannot yet conclude anything with high confidence.
Hence, the suggested action would be for the community to gather more votes and continue discussion around the proposal.
By utilizing a dynamic quorum, we can direct attention and participation of the community towards contentious proposals,
while reducing attention towards proposals which already have overwhelming support.

\subsubsection{Background}
A population of voters (a community) needs to collectively decide which item (if any) to take action on out of a set of competing items.
In order to democratically take action, the population needs to have a \{simple, super\}-majority of ``yes'' votes on a
winning item, while also demonstrating that the winning item is preferred over all other competing items.
We do not want to poll the entire population, but we do want to be certain (specifically, $99\%$ certain) that
the population does not take undesired actions, which in this case encompasses taking action on an item that is not
supported by a majority of the population and/or taking action on an item that is not clearly preferred over all
other competing alternatives.

\subsubsection{Problem Statement}
We wish to compute the probability that the bias in a population towards voting ``yes'' is greater than some
fraction of the population (e.g., $50\%$ for a simple majority, $67\%$ for a super majority).
In addition, we wish to compute the probability that the bias towards voting ``yes'' on a specific item is greater
than the bias towards voting ``yes'' on all other competing items.

\subsubsection{Assumptions}
We assume that there is a fixed underlying bias in the population that is to be estimated given raw voting data.

Without any votes, we assume that this bias may be any value between $0\%$ and $100\%$ with equal probability.

\subsubsection{Voting}
We allow for range voting where each member of the population may choose any real number in the range $[-1,+1]$ to
represent their vote, with $-1$ representing opposition and $+1$ representing support.
In the theory subsection below, we rescale votes to be in the range $[0,1]$ via the notation $\frac{votes + 1}{2}$.

We allow voters to ``abstain'' from voting.
We treat abstentions as indicating that a voter is removing themselves from the population of voters for an item.
It is important to distinguish an ``abstention'' (removing yourself from the voting population) from voting $0$
(indicating indifference).

\subsubsection{Bayesian Theory}

The commonplace and convenient choice of using the Beta distribution as our prior on the population bias is a
consequence of the Beta distribution's conjugacy with the binomial distribution, a distribution that arises
naturally when considering samples from a finite population.\footnote{To
properly understand the Bayesian approach to parameter estimation, read the following instructive tutorial:
\url{http://www.behind-the-enemy-lines.com/2008/01/are-you-bayesian-or-frequentist-or.html}
The tutorial is very similar to the problem we have at hand.}

After extracting the sufficient statistics from raw votes~---~namely the average score and the number of
abstentions~---~we can adjust the effective population size and corresponding threshold.
In addition, we can calculate the effective number of ``yes'' and ``no'' votes.\footnote{Which one can think
of as the number of Heads and Tails in the aforementioned tutorial.}

Let
\begin{description}
\begin{itemize}
\item[$C = $] $\{X_1,\ldots, X_n\}$, the set of competing motions,
\item[$N = $] population size,
\item[$X_i = $] $\{v_1, \ldots, v_{m_i}\}$, the $m_i$ raw votes for motion $X_i$, excluding ``abstentions'',
\item[$N_i = $] $(N - \textrm{number of abstentions on } X_i)$, the effective population voting on motion $X_i$,
\item[$\alpha_i = $] $\sum\limits_{v \in X_i} \left(\frac{v+1}{2}\right)$, the effective number of ``yes'' votes on motion $X_i$,
\item[$\beta_i = $] $m_i - \alpha_i$, the effective number of ``no'' votes on motion $X_i$,
\item[$K_i = $] $N_i - m_i$, the number of remaining votes yet to be cast on $X_i$,
\item[$p_i = $] true latent population bias towards voting ``yes'' on $X_i$.
\end{itemize}
\end{description}

When we have a single motion open for voting, $C=\{X_1\}$, we simply wish to compute:
\begin{align}\label{eq1}
\Pr(\alpha^*_1 > T_1 \mid X_1),
\end{align}
where
\begin{description}
\begin{itemize}
\item[$\alpha^*_i = $] the total number of ``yes'' votes for $X_i$ if we were to sample the entire population,
\item[$T_i = $] $f \cdot N_i$, for some fraction $f$ corresponding to the type of majority needed for the vote
(e.g. $f=\frac{1}{2}$ for a simple majority).
\end{itemize}
\end{description}
Using the prior $p_1 \mid X_1 \sim \operatorname{Beta}(1+\alpha_1,1+\beta_1)$, corresponding to a uniform prior when
no votes have been cast ($\alpha_1 = \beta_1 = 0$), we can express \eqref{eq1} as:
\begin{align*}
\Pr(\alpha^*_1 > T_1 \mid X_1) &= 1 - \Pr(\alpha^*_1 \leq T_1 \mid X_1),\\
\Pr(\alpha^*_1 \leq T_1 \mid X_1) &= \int_0^1 \Pr(\alpha^*_1 \leq T_1 \mid p_1)\cdot \Pr(p_1 \mid X_1) \mathrm{d}p_1\\
&= \int_0^1 \sum\limits_{i=0}^{V_1} {K_1 \choose i} p_1^{i} {(1-p_1)}^{K_1-i} \\
& \qquad\qquad\quad \times \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \mathrm{d}p_1,
\end{align*}
where
\begin{description}
\begin{itemize}
\item[$V_i = $] $\lfloor{T_i - \alpha_i}\rfloor$, the maximum number of additional ``yes'' votes allowed such that
$X_i$ would remain below threshold.
\end{itemize}
\end{description}

Hence, we have
\begin{align}\label{eq2}
& \Pr(\alpha^*_1 > T_1 \mid X_1) = \nonumber\\
& 1 - \int_0^1 \sum\limits_{i=0}^{V_1} {K_1 \choose i} p_1^{i} {(1-p_1)}^{K_1-i} \cdot \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \mathrm{d}p_1
\end{align}

In the scenario where $\mathbf{card}(C) = n > 1$, i.e., there are competing motions, there is additional complexity to
consider.
Without loss of generality, assume that $X_1$ is the most popular motion within $C$.
We now wish to not only compute \eqref{eq1}, but also the probability that $X_1$ is superior to all other
$X_i  \in C, i \neq 1$:

\begin{align}\label{eq3}
\Pr\left(\bigwedge_{i=2}^n (\alpha^*_1 > \alpha^*_i) \mid C\right)
\end{align}

Using the assumption
that votes on motions are independent across motions, which, in the common
scenario where there is a negative covariance between votes on competing
motions, will provide a lower bound on the probability, we can decompose \eqref{eq3} as follows:
\begin{align*}
& \Pr\left(\bigwedge_{i=2}^n (\alpha^*_1 > \alpha^*_i) \mid C\right)\\
=& \prod_{i=2}^n \Pr(\alpha^*_1 > \alpha^*_i \mid C)\\
=& \prod_{i=2}^n \iint\limits_{p_1, p_i} \Pr(\alpha^*_1 > \alpha^*_i \mid p_1, p_i) \cdot \Pr(p_1 \mid X_1) \cdot \Pr(p_i \mid X_i) \mathrm{d}p_i \mathrm{d}p_1\\
=& \prod_{i=2}^n \int_0^1 \int_0^1 \Pr(\alpha^*_1 > \alpha^*_i \mid p_1, p_i) \cdot \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \\
& \qquad\qquad\qquad \times \operatorname{Beta}(p_i; 1+\alpha_i,1+\beta_i) \mathrm{d}p_i \mathrm{d}p_1\\
\end{align*}
Deriving an expression for $\Pr(\alpha^*_1 > \alpha^*_i \mid p_1, p_i)$, we get:
\begin{align*}
& \Pr(\alpha^*_1 > \alpha^*_i \mid p_1, p_i)\\
=& 1 - \Pr(\alpha^*_1 \leq \alpha^*_i \mid p_1, p_i)\\
=& 1 - \sum\limits_{m=0}^{K_1} \sum\limits_{n=\lceil{v_{1,i}+m}\rceil}^{K_i} {K_1 \choose m} p_1^{m} {(1-p_1)}^{K_1 - m} \cdot {K_i \choose n} p_i^{n} {(1-p_i)}^{K_i-n},
\end{align*}
where
\begin{description}
\begin{itemize}
\item[$v_{i,j} = $] $\alpha_i - \alpha_j$, the number of effective ``yes'' votes $X_i$ leads $X_j$ by.
\end{itemize}
\end{description}

Denoting
\begin{align}\label{eq4}
& \Phi_i(p_1,p_i) {\overset {\underset {\mathrm {def} }{}}{=}} \nonumber\\
& 1 - \sum\limits_{m=0}^{K_1} \sum\limits_{n=\lceil{v_{1,i}+m}\rceil}^{K_i} {K_1 \choose m} p_1^{m} {(1-p_1)}^{K_1 - m} \cdot {K_i \choose n} p_i^{n} {(1-p_i)}^{K_i-n},
\end{align}
we can simplify \eqref{eq3} to:
\begin{align}\label{eq5}
& \Pr\left(\bigwedge_{i=2}^n (\alpha^*_1 > \alpha^*_i) \mid C\right)\nonumber\\
&= \prod_{i=2}^n \int_0^1 \int_0^1 \Phi_i(p_1,p_i) \cdot \operatorname{Beta}(p_1; 1+\alpha_1,1+\beta_1) \nonumber\\
& \qquad\qquad\qquad \times \operatorname{Beta}(p_i; 1+\alpha_i,1+\beta_i) \mathrm{d}p_i \mathrm{d}p_1
\end{align}

We can numerically compute \eqref{eq2} and \eqref{eq5} given raw voting data.
In order to be certain before taking any actions, we would like for the computed credibilities to be $\geq 99\%$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/simple_majority}
\caption{Simple Majority: $\alpha$ vs. $\Pr(\alpha > \frac{1}{2}N)$ for $N=100$, $\beta = 10$.}
\label{simple_majority}
\end{figure}
%Data:
%Curve 1: {{0,0.000299648},{1,0.00213083},{2,0.00817989},{3,0.0224777},{4,0.049512},{5,0.0928927},{6,0.154136},{7,0.232044},{8,0.322859},{9,0.421057},{10,0.520467},{11,0.615358},{12,0.701241},{13,0.775267},{14,0.836245},{15,0.884385},{16,0.920892},{17,0.947532},{18,0.966265},{19,0.978973},{20,0.987296},{21,0.992561},{22,0.99578},{23,0.997682},{24,0.998767},{25,0.999366}}
%Curve 2: {x, 0.99} for all x

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/super_majority}
\caption{Super Majority: $\alpha$ vs. $\Pr(\alpha > \frac{2}{3}N)$ for $N=100$, $\beta = 10$.}
\label{super_majority}
\end{figure}
%Data:
%Curve 1: {{10,0.0395173},{11,0.0591278},{12,0.0846131},{13,0.116407},{14,0.15463},{15,0.199057},{16,0.24911},{17,0.303899},{18,0.362273},{19,0.422909},{20,0.484399},{21,0.545345},{22,0.604445},{23,0.660559},{24,0.712764},{25,0.760382},{26,0.802985},{27,0.840385},{28,0.872612},{29,0.899875},{30,0.922519},{31,0.940987},{32,0.955777},{33,0.967407},{34,0.976384},{35,0.983186},{36,0.988243},{37,0.99193},{38,0.994567},{39,0.996414},{40,0.997682},{41,0.998533},{42,0.999093},{43,0.999452},{44,0.999677},{45,0.999815},{46,0.999896},{47,0.999944},{48,0.99997},{49,0.999985},{50,0.999993}}
%Curve 2: {x, 0.99} for all x

%\todo[inline]{Do we take into the account the distribution of votes? So if you have a very large standard deviation
%we might want to prefer a decision less than some other decision with smaller standard deviation, but maybe
%also smaller (but still positive) average. Is distribution of votes influencing dynamic quorum?}
